---
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ADSC1010 Final Project Report

### THOMPSON RIVERS UNIVERSITY

------------------------------------------------------------------------

## DATA VISUALISATIONS  IN R

------------------------------------------------------------------------

  Vishesh Khurana (T00732605)

  ADSC1000 Statistical Analysis

  Prof. Sean Hellingman

\doublespacing

## CONTENTS

1.  Head shot percentages for plots:

    1.  Team With Best Head Shot percentage.
    2.  Which Team had the Highest Head shot Percentage Against them.

2.  Bar Plot of the most played agents in the League by Player Name.

3.   Scatter Plot of 1v1 fights in the Playoffs.

4.   Violin Plots of Player head shot percentages by team.

5.   First Kills per Round Percentage to First Kill (For Duelists and Controllers)

6.   Pie Plot of number of Initiator type agents played.

7.   [Appendix]


## DATA INTRODUCTION

This is the data of the whole season of Valorant Esports for their Pacific League.

There are 3 tables.
- player_stats : Which has player statistics for players for every single match
  they have played throughout the season.
- leaderboard : The leader board of the season.
- 1v1 stats: this table has 1v1 fight stats of all the players against other 
  players.
  
* The data is used to make useful insights about the amazing season of Pacific 
 Valorant.

* These Insights could be used to scout players for the next season or just to
  Analyse this season's influential facts.


Attributes from the data are:

1. player_name : Player Name
2. team: team name
3. opponent: opponent for the each match
4. rating: player rating for the match.
5. acs: Average combat score for the match.
6. kill: total kills for the match.
7. death: total deaths for the match.
8. hs_percent: Headshot percentages of the match.
9. first_kill: total first kills in the match.
10. first_dealth: total first deaths in the match.
11. map: on which map the game was played
12. various score columns showing the exact scores.
13: game tracking id's and player ids
14: role_agent: the role of the character players played.
15: agent: The name of the agent played by the player.


- 1v1 table has similar attributes but for different 1v1 fights.


```{r include=FALSE}
#Libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(car)
library(tibble)
library(plotly)
```
* Loaded all the files and manipulated some columns for ease of use.
* Added a few metrics to be able to plot meaningful data.
```{r include= FALSE}
player_p_stats<- read.csv(file="player_stats.csv")
leaderboard<- read.csv(file="team_stats.csv")
one_stats<- read.csv(file="1v1.csv")

#FUNCTION
sepp<- function(data,charZ,charX,charY){
  return (separate(data,charZ,c(charX,charY),sep = "%"))
  }

player_p_stats<-player_p_stats %>%
  sepp(.,"hs_percent","HS_per","Percentage") %>%
  select(-Percentage) %>% 
  mutate_at(c("HS_per"),as.numeric) %>%
  arrange(-HS_per) %>% 
  mutate(HS_per=HS_per/100) %>% 
  group_by(player_name) %>% 
  mutate(total_rounds_played= sum(total_round),
         total_FK= sum(first_kill),
         FK_per_round= total_FK/total_rounds_played) 
  
```

Calculated  the aggregated head shots percentages of the teams and
sorted it via the team mean.
```{r include= FALSE}
#Team With Best Head Shot percentage

highest_hd_team<- player_p_stats %>% 
  group_by(team) %>%
  filter(total_rounds_played>250) %>% 
  summarise(team_mean=mean(HS_per)) %>% 
  arrange(-team_mean)
```


Created the Scatterplot of the teams vs headshot percentages.
```{r p1}
plot.1<- ggplot(data=highest_hd_team)+
  geom_point(aes(y= team_mean, x=team))+
  labs(title="ScatterPlot Showing the Teams With Best Head Shot percentage ",
       xlab="Team",
       ylab="HS percentage of Team")+
  annotate("text",x=9.2,y=0.275,label="(Min 250 Rounds<br>Played)")

ggplotly(plot.1)


```

- This Scatter Plot shows which of the Players are cracked at aiming.
- Team DFM had the highest mean head shot percentage (0.276), while team 
  TS had the least.(0.233)

```{r include= FALSE}
#Highest Head shot percentages against which team

highest_hd_opp <- player_p_stats %>% 
  group_by(opponent) %>% 
  filter(total_rounds_played>250) %>% 
  summarise(opp_mean=mean(HS_per)) %>% 
  arrange(-opp_mean)


highest_hd_opp
```


Created the ScatterPlot of the Teams vs their opponent's headshot percentages
against them.
```{r}
plot.2<-ggplot(highest_hd_opp,aes(y= opp_mean, x=opponent))+
  geom_point()+
  labs(title="ScatterPlot - Which team got headshot the most",
       xlab="Team",
       ylab="mean HS percentage")+
  annotate("text",x=9.2,y=0.262,label="(Min 250 Rounds<br>Played)")

ggplotly(plot.2)

```

- This Scatter Plot Shows which team was getting out aimed from their opponents.
- Team PRS and GES were getting Head shotted alot during their games.
- This can also show that they're maybe one of the best aiming teams, which requires the other team to shoot better.

```{r include= FALSE}
# Who has played most agents in the whole tournament


Agent_stats<-player_p_stats %>% 
  group_by(player_name) %>% 
  distinct(agent) %>% 
  count(player_name) %>% 
  arrange(-n) %>% 
  rename("agents_played"="n") 

unique_players<-unique(player_p_stats[c("player_name","team")])
        
               
Agents_Played<- Agent_stats %>% 
  right_join(unique_players, by="player_name") %>% 
  head(12)
```

#Created a Barplot of the most played agents in the League.
```{r }
ggplot(data= Agents_Played, aes(y=player_name,x=agents_played,fill=team))+
  geom_col()+
  scale_x_continuous(breaks = 1:10)+
  labs(title="Most Played Agents by Players",
       xlab="No of Agents",
       ylab="Player_Names")


```

- This Bar Plot shows that F0rsakeN has played the most Agents(Characters) in the whole league followed by Rb and Patt.

```{r include= FALSE}
#Scatter Plot of 1v1 Fights

one_stats$index<- 1:nrow(one_stats)
uniq<- unique(one_stats$tourney_type) 

one_Playoffs_duel<- one_stats %>% 
  filter(tourney_type==uniq[9:13],) %>%  #Only selected playoffs
  mutate(kd= kill/death)

one_Playoffs_duel
```

Scatterplot of the 1v1 fights won by players in the playoffs.
```{r}
plot_ly(data=one_Playoffs_duel,
        x=~kd,
        y=~player,
        type="scatter",
        text = ~paste("Vs ", opponent, 
                       '<br>Kill:',kill,"Death:",death 
                      ,'<br>Team', team)
        ) %>% 
  layout(title="Scatter Plot of Who won the most 1v1 Fights")

```
- This Scatter Plot shows the best 1v1 performances in a a single match.
- D4v4i executed Carpe 7 times and in return got killed only once, 
  in their ingame encounter.



#ViolinPlot of the Headshot Percentages of Different Teams.
```{r}
#Voilin Plot of Headshot Percentages of different teams

violin.plot<-ggplot(data=player_p_stats, aes(x=team,y=HS_per)) +
  geom_violin(trim=FALSE)+
  stat_summary(fun.data =mean_sdl,mult=1,geom="pointrange")+
  labs(title="Violin Plot of Headshot Percentages of Different Teams",
       xlab="Teams",
       ylab="HS Percentage")

ggplotly(violin.plot)
```
- Violin Plot here shows the Headshot Percentage Peaks in the Data as Well as the Distribution of the Percentages in each team.
- There is also a mean point which shows, the mean hs percentage for each team.


```{r include= FALSE}
#First Kills per Round Percentage to First Kill (For Duelists)

df.duel.fk<- player_p_stats %>% 
  filter(total_rounds_played>400, role_agent=="Duelist") %>% 
  distinct(player_name, .keep_all = TRUE)
```


# ScatterPlot of First Kills vs FK per Round for the Agent Role: Duelist.
```{r}
plot_ly(data=df.duel.fk,
        x=~first_kill,
        y=~FK_per_round,
        color=~team,
        type="scatter",
        text = ~paste("Player Name: ", player_name, 
                      '<br>FK per round:', FK_per_round, 
                      '<br>Team', team)
        ) %>% 
  layout(title="First Kills vs FK per Round for thr Role of Duelist")


```

- This Graph shows the best player at getting first kills along with their First Kill per round rate for only the duelist role.
- Player Foxy9 from DRX seems to be the best at first kills.

```{r include= FALSE}
#First Kills per Round Percentage to First Kill (For Controllers)

most_played<- function(data){
  data %>% 
    group_by(player_name) %>% 
    count(agent)
  return()
}


df.ctrl.fk<- player_p_stats %>% 
  filter(total_rounds_played>400, role_agent=="Controller") %>% 
  distinct(player_name, .keep_all = TRUE)

df.ctrl.fk
```

# ScatterPlot of First Kills vs FK per Round for the Agent Role: Controller.
```{r}
plot_ly(data=df.ctrl.fk,
        x=~first_kill,
        y=~FK_per_round,
        color=~team,
        type="scatter",
        text = ~paste("Player Name: ", player_name, 
                      '<br>FK per round:', FK_per_round, 
                      '<br>Team', team)
        
        ) %>% 
  layout(title="First Kills vs FK per Round for thr Role of Controllers")


```

- Controller is the most important in the defense, hence with this chart we can tell that who gets the first kill no matter what.
- - This Graph shows the best player at getting first kills along with their First Kill per round rate for only the Controllers.
- According to the graph Ts gets the first kill very oftenly although per round he is bad cause he has played alot of rounds.

```{r include= FALSE}
#Pieplot of no of agents played

player_p_stats
no.of.agents<- player_p_stats %>% 
  filter(role_agent=="Initiator") %>% 
  count(agent) %>% 
  arrange(-n) %>% 
  rename("agents_played"="n") %>% 
  select(agent,agents_played)
```

# Pie Plot of number of Initiator type agents played.
```{r}
plot_ly(data=no.of.agents,
        type="pie",
        labels=~agent,
        values=~agents_played,
        textinfo="label",
        insidetextorientation='radial'
        ) %>% 
  layout(
    title="Pie Chart of Initiator Type times Agents were played"
  )
```

- The Pie Plot Shows the most played Initiator Agents in the Tournament.
- Skye is the most played Agent according to the plot with 27.6% pick rate.







### APPENDIX


```{r}
player_p_stats<- read.csv(file="player_stats.csv")
leaderboard<- read.csv(file="team_stats.csv")
one_stats<- read.csv(file="1v1.csv")

#FUNCTION
sepp<- function(data,charZ,charX,charY){
  return (separate(data,charZ,c(charX,charY),sep = "%"))
  }

player_p_stats<-player_p_stats %>%
  sepp(.,"hs_percent","HS_per","Percentage") %>%
  select(-Percentage) %>% 
  mutate_at(c("HS_per"),as.numeric) %>%
  arrange(-HS_per) %>% 
  mutate(HS_per=HS_per/100) %>% 
  group_by(player_name) %>% 
  mutate(total_rounds_played= sum(total_round),
         total_FK= sum(first_kill),
         FK_per_round= total_FK/total_rounds_played) 
  
head(player_p_stats)
```

```{r}
#Team With Best Head Shot percentage

highest_hd_team<- player_p_stats %>% 
  group_by(team) %>%
  filter(total_rounds_played>250) %>% 
  summarise(team_mean=mean(HS_per)) %>% 
  arrange(-team_mean)
head(highest_hd_team)
```


```{r}
#Highest Head shot percentages against which team

highest_hd_opp <- player_p_stats %>% 
  group_by(opponent) %>% 
  filter(total_rounds_played>250) %>% 
  summarise(opp_mean=mean(HS_per)) %>% 
  arrange(-opp_mean)


head(highest_hd_opp)
```



```{r}
# Who has played most agents in the whole tournament


Agent_stats<-player_p_stats %>% 
  group_by(player_name) %>% 
  distinct(agent) %>% 
  count(player_name) %>% 
  arrange(-n) %>% 
  rename("agents_played"="n") 

unique_players<-unique(player_p_stats[c("player_name","team")])
        
               
Agents_Played<- Agent_stats %>% 
  right_join(unique_players, by="player_name") %>% 
  head(12)

Agents_Played
```


```{r}
#Scatter Plot of 1v1 Fights

one_stats$index<- 1:nrow(one_stats)
uniq<- unique(one_stats$tourney_type) 

one_Playoffs_duel<- one_stats %>% 
  filter(tourney_type==uniq[9:13],) %>%  #Only selected playoffs
  mutate(kd= kill/death)

head(one_Playoffs_duel)
```


```{r}
#First Kills per Round Percentage to First Kill (For Duelists)

df.duel.fk<- player_p_stats %>% 
  filter(total_rounds_played>400, role_agent=="Duelist") %>% 
  distinct(player_name, .keep_all = TRUE)

head(df.duel.fk)
```


```{r}
#First Kills per Round Percentage to First Kill (For Controllers)

most_played<- function(data){
  data %>% 
    group_by(player_name) %>% 
    count(agent)
  return()
}


df.ctrl.fk<- player_p_stats %>% 
  filter(total_rounds_played>400, role_agent=="Controller") %>% 
  distinct(player_name, .keep_all = TRUE)

head(df.ctrl.fk)
```


```{r}
#Pieplot of no of agents played

player_p_stats
no.of.agents<- player_p_stats %>% 
  filter(role_agent=="Initiator") %>% 
  count(agent) %>% 
  arrange(-n) %>% 
  rename("agents_played"="n") %>% 
  select(agent,agents_played)

head(no.of.agents)

#Realized very late that we had to use loop.
#Using loop to show that I know how to use them.


toss <- c("head","tail")
for(x in toss) {
  if (x == "head") {
    print(paste("First It's", x))
  } else {
    print(paste("Second It's", x))
  }
}
```


